---
title: "Regression Models Project"
output: pdf_document
---
This project uses regression in R to address the following re the mtcars dataset: (1)If automatic or manual transmission is better for MPG, and (2) A quantification of the MPG difference between automatic and manual transmissions.
```{r}
library(datasets)
data(mtcars)
attach(mtcars)
fit1 <- lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am + gear + carb)
confint(fit1)
```
confint(fit1)'s output suggests candidates for elimination from an updated model: cyl, drat, vs, gear, and carb have 95% confidence intervals split relatively evenly by the number 0, unlike wt, whose interval lies mostly on one side.
```{r}
fit2 <- lm(mpg ~ disp + hp + wt + qsec + am)
confint(fit2)
```
We can compare fit1 and fit2 using anova() and the AIC.
```{r}
anova(fit2, fit1)
AIC(fit1, fit2)
```
Both tests favor fit2: anova because the testing added by the discarded variables to the linear prediction is insignificant (since p = 0.97); AIC because the AIC value for fit2 is much smaller than for fit1.  confint(fit2) reveals that the beta coefficients for disp and hp are to p > 95% not big enough to have a noticeable effect on mpg.
```{r}
fit3 <- lm(mpg ~ wt + qsec + am)
confint(fit3)
```
Finally, we should consider interactions among the explaning variables in fit3.  For brevity's sake, we first find the correlations among the variables as a general measure of each pair's interactivity.
```{r}
cor(wt, qsec)
cor(wt, am)
cor(qsec, am)
```
The only pair that we should integrate into the model is wt:am (because magnitude of cor(wt,am) much higher than other two values).
```{r}
fit4 <- lm(mpg ~ wt + qsec + am + wt:am)
summary(fit4)[8:9]
```
summary(fit4) supports the choice of fit4 in that the un-adjusted R-squared value is 0.89 (adjusted, 0.88), thereby suggesting that fit4 "explans" about that proportion of the total variance from the population mean.
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(fit4)
```



